---
output: html_document
---

## Exercise 2.8

__This exercise relates to the "College" data set, which can be found in the file "College.csv". It contains a number of variables for 777 different universities and colleges in the US.__

a. __Use the read.csv() function to read the data into R. Call the loaded data "college". Make sure that you have the directory set to the correct location for the data.__

We can read the data directly from the StatLearning website using the call shown below

```{r}
college <- read.csv("https://www.statlearning.com/s/College.csv")
```

b. __Look at the data using the `fix()` function. You should notice that the first column is just the name of each university. We don’t really want R to treat this as data. However, it may be handy to have these names for later.__

The `fix()` function opens a window on our machine - to ensure reproducibility we instead use `head()` to view the first 20 rows

```{r}
head(college[, 1:5], n = 20)
```

We can remove the university names from the data set - while not completely getting rid of these names using the code shown in the following chunk

```{r}
## Enter your code below
```

c. __Use the `summary()` function to produce a numerical summary of the variables in the data set.__

The code below is a concise way to:

1. Apply the `summary()` function to each column in the data set
2. Combine these summaries together in a data frame 
3. Output the data frame as a table 

```{r}
knitr::kable(as.data.frame(do.call(cbind, lapply(college, summary))))
```

__Use the `pairs()` function to produce a scatterplot matrix of the first ten columns or variables of the data.__

<!-- enter your solution here -->

__Create a new qualitative variable, called "Elite", by binning the "Top10perc" variable. Use the `summary()` function to see how many elite universities there are. Now use the `plot()` function to produce side-by-side boxplots of "Outstate" versus "Elite".__

The `Elite` column is created as shown below

```{r}
Elite <- rep("No", nrow(college))
Elite[___________] <- "Yes"
Elite <- as.factor(Elite)
college$Elite <- Elite
summary(college$Elite)
```

The requested boxplot is generated as shown below

```{r}
## Replace this comment with your code to generate the boxplot 
```

__Use the `hist()` function to produce some histograms with numbers of bins for a few of the quantitative variables.__

In the code chunk below we generate histograms for four of the variables in this data set and present them as a $2 \times 2$ grid of plots

```{r}
par(mfrow = c(2,2), las = 1)

hist(_________, 
     col = 2, 
     xlab = "Books", 
     ylab = "Count",
     border = "white",
     main = "")

hist(_________, 
     col = 3, 
     xlab = "PhD", 
     ylab = "Count",
     border = "white",
     main = "")

hist(_________, 
     col = 4, 
     xlab = "Grad Rate", 
     ylab = "Count",
     border = "white",
     main = "")

hist(_________, 
     col = 6, 
     xlab = "% alumni", 
     ylab = "Count",
     border = "white",
     main = "")
```

__Continue exploring the data, and provide a brief summary of what you discover.__

<!-- Put whatever you want here -->

