---
output: html_document
---

## Exercise 3.8

__This question involves the use of simple linear regression on the `Auto` data set.__

a. __Use the `lm()` function to perform a simple linear regression with mpg as the response and horsepower as the predictor. Use the `summary()` function to print the results. Comment on the output. For example:__

```{r}
library(ISLR)
data(Auto)

lm.fit <- lm(___ ~ ___, 
             data = Auto)

knitr::kable(broom::tidy(summary(lm.fit)))
```


i. __Is there a relationship between the predictor and the response?__

<!-- enter your solution here -->

ii. __How strong is the relationship between the predictor and the response?__

<!-- enter your solution here -->

iii. __Is the relationship between the predictor and the response positive or negative?__

<!-- enter your solution here -->
    
iv. __What is the predicted mpg associated with a horsepower of 98? What are the associated 95 % confidence and prediction intervals?__

```{r}
.new_data = _______________

predict(lm.fit, 
        newdata = .new_data, 
        interval = "confidence")

predict(lm.fit, 
        newdata = .new_data, 
        interval = "prediction")
```

b. __Plot the response and the predictor. Use the `abline()` function to display the least squares regression line.__

```{r}
plot(x = ___________, 
     y = ___________,
     pch = 16,
     col = scales::alpha("black", alpha = 0.25))

abline(lm.fit, 
       lwd = 3, 
       col = 2)
```

c. __Use the `plot()` function to produce diagnostic plots of the least squares regression fit. Comment on any problems you see with the fit.__

```{r}
par(mfrow = c(2,2))

plot(lm.fit)
```
