---
output: html_document
---

## Exercise 4.12

__This problem involves writing functions.__

a. __Write a function, `Power()`, that prints out the result of raising 2 to the 3rd power. In other words, your function should compute $2^3$ and print out the results.__


```{r]
Power <- function(){

2^3

}

Power()
```
b. __Create a new function, `Power2()`, that allows you to pass any two numbers, "$x$" and "$a$", and prints out the value of "$x^a$".__
```
```{r}
Power2= function(x = 3, a =7) {

x ^ a

}

Power2()
Power2(5,8)
```
c. __Using the `Power2()` function that you just wrote, compute $10^3$, $81^7$, and $131^3$.__

<!-- enter your solution here -->

d. __Now create a new function, `Power3()`, that actually returns the result "$x^a$" as an R object, rather than simply printing it to the screen. That is, if you store the value "$x^a$" in an object called "result" within your function, then you can simply `return()` this result.__

```{r}
Power3= function(x = 3, a = 7) {

return(x ^ a)

}

ans = Power3()

ans
```
e. __Now using the `Power3()` function, create a plot of $f(x)=x \cdot 3$. The x-axis should display a range of integers from 1 to 10, and the y-axis should display $x^2$. Label the axes appropriately, and use an appropriate title for the figure. Consider displaying either the x-axis, the y-axis, or both on the log-scale.__

```{r}
x <- 1:10
y <- Power3(x, a = 3)

x
y

plot(x = x, 
y = y,
xlab = "x",
ylab = "x^3")

plot(x = x, 
y = y,
xlab = "x",
ylab = "x^3",
type = "1")
```

f. __Create a function, `PlotPower()`, that allows you to create a plot of "$x$" against "$x^a$" for a fixed "$a$" and for a range of values of "$x$".__
```
```[r]
PlotPower= function(x, a){

y = x^a
plot(x=x, y=y, xlab = "x", ylab = "x^3)

}

PlotPower(x = 1:10, a = 3)
```
